% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

    % Set the page margins.
    \usepackage[a4paper,margin=0.75in]{geometry}
    
    % Setup the language.
    \usepackage[english]{babel}
    \hyphenation{Some-long-word}
    
    % Makes resume-specific commands available.
    \usepackage{style/resume2pages}
    
    
    
    
    \begin{document}  % begin the content of the document
    \sloppy  % this to relax whitespacing in favour of straight margins
    
    
    % title on top of the document
    \maintitle{Cies Breijs}{June 12, 1982}{Last update on \today}
    
    \nobreakvspace{0.3em}  % add some page break averse vertical spacing
    
    % \noindent prevents paragraph's first lines from indenting
    % \mbox is used to obfuscate the email address
    % \sbull is a spaced bullet
    % \href well..
    % \\ breaks the line into a new paragraph
    \noindent\href{mailto:cies.at.kde.dot.nl}{cies\mbox{}@\mbox{}kde.nl}\sbull
    \textsmaller{+}31.646469087\sbull
    \href{https://github.com/cies}{github.com/cies}\sbull
    \href{http://linkedin.com/in/ciesbreijs}{linkedin.com/in/ciesbreijs}
    \\
    Mathenesserplein 84\sbull
    3022\thinspace {\large \sc ld}\sbull
    Rotterdam\sbull
    The Netherlands
    
    \spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after
    
    \roottitle{Summary}  % a root section title
    
    \vspace{-1.3em}  % some vertical spacing
    \begin{multicols}{2}  % open a multicolumn environment
    \noindent \emph{Entrepeneurial geek with roots in the open source movement. Passionately enabling software-related teams to deliver. Creates/\,structures/\,improves processes. Architects and helps to implement future-proof solutions. Coaches both individuals and groups.}
    \\
    \\
    At the age of seven (1989) Cies wrote his first lines of code in a \acr{LOGO}-like language on an \acr{MSX} (pre-\acr{PC}).  Two years later he attended a conference on an emerging new technology, the Internet, at the Erasmus University from which he would graduate 16 years later (2000) with a degree in Business Computer Science.
    
    After being introduced to the open source movement in 1997, he taught himself a variety of skills including system administration and programming (Bash, Python, Ruby \& \CPP).  By 2002 he got his pet project \acr{KT}urtle ---a zero-entry-barrier programming environment--- included in \acr{KDE}'s \emph{edu} module, and thereby in almost every Linux distribution.
    
    Extensively travelled Europe and Asia after graduating. On return his professional life became a mix of hands-on work in startups and web software agencies, while settling as a husband and father in personal life.
    \end{multicols}
    
    
    \spacedhrule{0em}{-0.4em}
    
    \roottitle{Experience}
    
    \headedsection
      {\href{http://cies.breijs.com}{\acr{CIES.BREIJS.COM.}}}
      {\textsc{Rotterdam, The Netherlands}} {%
      \headedsubsection
        {Freelance \acr{IT} Consultant}
        {Oct \apo16 -- present}
        {\bodytext{Provides services related to software development, such as:\@ coaching, audits, process improvement, web/cloud architecture, recruitment strategy and tender advise.  Clients:\@ \href{http://www.burst-digital.com/en}{Burst}, \href{https://hoppinger.com}{Hoppiner} \& \href{http://bit4u.nl}{Bit4U}.}}
    }
    
    
    \vspace{-0.2em}
    \begin{center}
      \emph{\small Please refer to \href{http://www.linkedin.com/in/ciesbreijs}{Cies' LinkedIn profile} for a more complete list of work experience along with recommendations.}
    \end{center}
    
    
    \spacedhrule{-0.2em}{-0.4em}
    
    \roottitle{Education}
    
    
    
    \headedsection
      {\href{http://www.tudelft.nl/en}{Technical University Delft}}
      {\textsc{Delft, The Netherlands}} {%
      \headedsubsection
        {Industrial Design Engineering \textnormal{\textit{~(discontinued)}}}
        {2001 -- 2002} {}
    }
    
    \headedsection
      {\href{http://www.libanonlyceum.nl}{Libanon Lyceum}}
      {\textsc{Rotterdam, The Netherlands}} {%
      \headedsubsection
        {VWO \textnormal{~(Pre-University Secondary Education)}}
        {1994 -- 2000} {}
    }
    
    
    \spacedhrule{0.5em}{-0.4em}
    
    \roottitle{Skills}
    
    \inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
      {Technical expertise:}
      {Leading and recruiting teams of software engineers.  Big fan of Agile methodologies, continuous delivery and functional programming.  Enjoys writing Ruby/\nsp Python/\nsp Java/\nsp \CPP~and Haskell.  Solid knowledge of the full web technology stack.  Able to architect \textit{and} implement distributed/\acr{HA} systems.  Strong Linux administration skills (e.g.\ Bash scripting, Apache/\acr{NGINX}, Postgres/My/No\acr{SQL}, ElasticSearch).  Well experienced with virtualization/containerization (Docker/Kubernetes, \acr{KVM}, Xen and several \acr{AWS} solutions) and DevOps (Puppet).  Emacs user.}
    
    \vspace{0.5em}
    \inlineheadsection
      {Natural languages:}
      {Dutch \emph{(mother tongue)}, English \emph{(full professional proficiency)}, German \emph{(limited working proficiency)}, French \emph{(elementary proficiency)} and Mandarin Chinese \emph{(beginner)}.}
    
    
    \spacedhrule{1.6em}{-0.4em}
    
    \roottitle{Interests}
    
    \inlineheadsection
      {Non-exhaustive and in alphabetical order:}
      {art, Buddhism, cryptography, functional programming, Go (board game), history, music (from classical and jazz to Berlin-techno), \acr{NLP}, permaculture, philosophy, rock climbing, startups, travel, typography (e.g.\ graphic design, \LaTeX), \acr{UX}-design and vegan cuisine.}
    
    
    \end{document}
    