% !TEX program = xelatex
% This is my resume
% by ice1000

\documentclass{style/resume2}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yinsen Zhang}

\basicInfo{
  \email{ice1000kotlin@foxmail.com} \textperiodcentered\
  \phone{(+86) 180-8192-5082} \textperiodcentered\
  \github[ice1000]{https://github.com/ice1000}
  % \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Chengdu Foreign Languages School (CFLS)}, Chengdu, China}{2015.9 -- 2018.6}
\datedsubsection{\textbf{Pennsylvania State University (PSU)}, United States}{2018.8 -- current}

\section{\faUsers\ Work Experience}
\datedsubsection{\textbf{Sourcebrella Inc.}, Shenzhen, China}{2018.2 -- 2018.7}
\role{Intern}{Compiler Front-End, IDE Plugin Development}
\begin{itemize}
  \item Created IntelliJ/CLion/Eclipse integration of the Pinpoint analyzer, helped to create SonarQube plugin
  \item Created a multi-threading cross Java/Kotlin source code indexer, index Hadoop takes 4 minutes
  \item Modified clang-3.6 front-end to compile the blockchain project \href{https://github.com/EOSIO/eos} {eos} which is currently using clang-4.0
\end{itemize}

\section{\faGithubAlt\ Personal Projects}
% \datedsubsection{\textbf{FriceEngine}}{\url{https://icela.github.io/}}
% % \role{Kotlin, C\#, Racket, Ruby}{Founder and main contributer to the Kotlin/C\#/Ruby version}
% A multilingual, natively-written, easy-to-use game engine series.
% \begin{itemize}
%   \item Based on life cycle / utility APIs, based on each languages' built-in GUI framework,
%     easy to install.
%   \item GitHub issues / milestones are used as task / version managing tools, nice changelogs.
%   \item A JavaFX-based drag-and-drop GUI designer, generates multilingual codes for each language.
% \end{itemize}
\datedsubsection{\textbf{DevKt}}{\url{https://github.com/ice1000/dev-kt}}
Cross-platform lightweight code editor / Kotlin IDE.
\begin{itemize}
  \item Built-in Java/Kotlin highlights and completion, other languages can be supported via plugins (which can be easily transplanted from JetBrains IDE plugins). Has extra build \& run support for Kotlin.
  \item Flexible architecture, decoupled high-level logic with UI, migration to other UI frameworks is easy.
  \item Provides fine-grained highlight color and keymap settings, support hot reload.
\end{itemize}

\datedsubsection{\textbf{Lice language}}{\url{https://github.com/lice-lang/lice}}
% \role{Kotlin, Java}{Founder and main contributer}
Scalable programming language running on JVM.
\begin{itemize}
  \item Supports lambda with and lazy (call by need) / macro (call by name) / strict (call by value).
  \item About one-twentieth of Java's (Hotspot 8u151) performance in benchmark, and can perfectly interact with JVM languages, work with Java's built-in script engine.
  \item Provides CLI REPL with GHCi-style code completion/colored output and JetBrains IDE plugin supporting semantic-based highlights, completion, go-to-definition, rename, eval-and-replace, quick fixes, etc.
\end{itemize}

\datedsubsection{\textbf{Julia-IntelliJ}}{\url{https://github.com/ice1000/julia-intellij}}
Julia plugin for JetBrains IDE, compatible with all JetBrains products.
\begin{itemize}
  \item Semantic-based highlights, quick fixes, completion, special input mode for Unicode characters.
  \item Supports existing tools like DocumentFormat.jl, provide config file highlights, completion, and linter.
  \item Provides a visualized package manager that wraps the built-in one.
  \item Integration with other plugins, like provide Markdown highlights for doc strings.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faHeartO\ Achievements}
\datedline{\textbf{1 kyu} on
  \href{https://www.codewars.com/users/ice1000} {CodeWars},
  ranked \#31 on the whole site, primarily in Haskell}{Aug. 2017}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages}:
    \textbf{multilingual} (not limited to any specific language),
    and especially experienced in (not listed in order) Java/Kotlin/Dart/C++/C\#/Haskell/Agda

  % compiler theories
  \item \textbf{Compilers}:
    proficient in various Parser Generators, understand type systems and things like type inference and bytecode optimization

  % language Kotlin
  \item \textbf{Kotlin/Java}:
    \textbf{2 years} of experience,
    \textbf{4} projects collected in
    \href{https://kotlin.link/?q=ice} {Awesome Kotlin}

  \item \textbf{Formal Verification}:
    understand type-level programming and dependent types, familiar with Agda(\textbf{1 years} of experience) and F$\star$

  \item \textbf{JetBrains MPS}:
    \textbf{1 years} of experience,
    understand Language-Oriented Programming

  \item \textbf{IDE Toolings}:
    \textbf{1 years} of experience,
    familiar with the IntelliJ Platform infrastructure and overall architecture,
    also have some experience with Eclipse/SonarQube

  % platforms I am familiar with
  \item \textbf{Mobile Development}:
    \textbf{2 years} of experience,
    Android (Java, Kotlin), Fuchsia (Flutter)

  \item \textbf{Editors}:
    can adapt to any editors, normally use JetBrains IDEs, Emacs, Notepad++
\end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: \url{http://ice1000.org/} partly translated into English
  \item Bintray: \url{https://bintray.com/ice1000} published some useful JVM libraries
  \item IntelliJ Plugin developer: \url{https://plugins.jetbrains.com/author/10a216dd-c558-4aaf-aa8a-723f431452fb}
  \item Opensource contributions: \url{http://ice1000.org/opensource-contributions/} \\
    provide bug fixes/new features to organizations like \textbf{Microsoft, JetBrains, Ruby, Dropbox}
    and projects like \textbf{imgui, shields.io}
  \item StackOverflow: \url{http://stackoverflow.com/users/7083401/ice1000} \\
    privileged moderator, also active on \href{https://stackexchange.com/users/9532102/ice1000} {other StackExchange} sites
  \item Languages: English - fluent (TOEFL 100), Chinese - native speaker
  % https://raw.githubusercontent.com/ice1000/resume/master/resume.pdf
  \item Get the newest version of this resume: \url{https://tinyurl.com/y8xdlfug}
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}

